---
title: "Tidy Tuesday 4"
description: "Data Visualization of Maximum Weight of Pumpkin per State"
theme: cosmo
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE, error = TRUE)

library(dplyr) 
library(tidyverse) 
library(ggplot2)
library(ggmap)
library(maps)
library(ggthemes) 
library(plotly)
library(viridis)
library(gganimate)
library(RColorBrewer)
```

```{r}
pumpkins <- read.csv("C:/Users/kates/OneDrive/Desktop/Advanced_data_science/TidyTuesday/pumpkins.csv")

```

```{r}
pumpkins <- pumpkins %>%
  separate(id, into = c("year", "class"), convert = TRUE)
```


```{r}
states_map <- map_data("state")


pumpkins_map <- pumpkins %>%
  filter(country == "United States",
         year == 2021) %>%
  mutate(State = tolower(state_prov)) %>%
  group_by(year,
           State)%>%
  summarize(Max_weight = max(weight_lbs)) %>%
  mutate(Max_weight = as.integer(Max_weight), 
         year = as.character(year))



pumpkins_animate <- pumpkins_map %>%
  ggplot() + 
  geom_map(aes(map_id = State,
               fill = Max_weight), 
           color = "grey", 
           map = states_map) + 
  expand_limits(x = states_map$long, y= states_map$lat) + 
  theme_map() + 
  scale_fill_viridis_c() + 
                           theme_map() + 
                           theme(legend.background = element_blank()) +
  labs(title = "Max Weight of Pumpkins per US States in 2021",
       fill = "") 

ggplotly(pumpkins_animate)

 
  
```

Data collected from the Great Pumpkin Commonwealth which is an organization that encourages local farmers to cultivate large pumpkins and enter them into competitions. I thought that it would be interesting to compare the states to see if there were any patterns of large growth throughout the country. I used this color palette because the yellow is easy to see which could help identify a pattern of where the highest max weight pumpkins.
