---
title: "Tidy Tuesday 2"
description: "Second Tidy Tuesday assignment for Advanced Data Science in R. Kate's process of creating data visulization."
theme: cosmo
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE, error = TRUE)

library(tidyverse) 
library(ggplot2)
library(RColorBrewer)
library(extrafont)
```

```{r}
nominees_tt <- read_csv("C:/Users/kates/OneDrive/Desktop/Advanced_data_science/TidyTuesday/nominees_tt.csv")
```
```{r}
#unique(nominees_tt$distributor) # how to see all different variables 

nominees_tt %>%
  select(type,
         title,
         distributor,
         year) %>%
  filter(distributor == c('Hulu', 
                          'HBO Max', 
                          'Netflix',
                          'HBO',
                          'Disney+',
                          'Showtime', 
                          
                          'Peacock')) %>%
  group_by(distributor, 
           type) %>%
  mutate(Count = n()) %>%
  ggplot(aes(x = distributor, fill = type)) + 
  geom_bar() + 
  labs(title = "Nominations and Win Totals by Top 7 Streaming Services from 1957 - 2021", 
       x = "Distributor", 
       y = "") + 
  guides(fill = guide_legend(title = NULL)) + 
  theme_minimal() 

```
First graph I created, thinking I wanted to visualize some ratio/comparison between nominee and win rates. Overall, was not that informative and I wanted to reach deeper into the data. 


```{r}
nominees_tt %>%
  select(type,
         title,
         distributor,
         year) %>%
  filter(type == "Winner")%>%
  filter(distributor == c('Hulu', 
                          'HBO Max', 
                          'Netflix',
                          'HBO',
                          'Disney+',
                          'Showtime',
                          'Prime Video',
                          'Peacock')) %>%
  group_by(year, distributor) %>%
  mutate(Count = n()) %>%
  ggplot(aes(x = year, y = Count, color = distributor)) + 
  geom_point() + 
  theme_minimal() + 
  labs(title = "Emmy Win Totals by Top 6 Streaming Services from 1995 - 2021", 
       x = "", 
       y = "") + 
  guides(fill = guide_legend(title = NULL))+ 
  theme(panel.grid.major.x = element_blank(), 
        plot.title = element_text(family = "A", hjust = 0.5))
```
Second graph I created was more interesting and I believe showed similar data that was related to the first graph, but instead showing the win ratios between the streaming services. Didn't like the geom_point().


\
\
\

***TIDY TUESDAY WK 2***

```{r}
windowsFonts(A = windowsFont("Times New Roman"))

nominees_10 <- nominees_tt %>%
  filter(year >2000)


nominees_10 %>%
  mutate(year = as.factor(year)) %>%
  select(type,
         title,
         distributor,
         year) %>%
  filter(type == "Winner")%>%
  filter(distributor == c('Hulu', 
                          'HBO Max', 
                          'Netflix',
                          'HBO',
                          'Disney+',
                          'Showtime',
                          'Prime Video',
                          'Peacock')) %>%
  group_by(year, distributor) %>%
  mutate(Count = n()) %>%
  ggplot(aes(x = year, fill = distributor)) + 
  geom_bar(position = "stack") + 
  theme_minimal() + 
  scale_fill_brewer(palette = "Set2") + 
  labs(title = "Emmy Win Totals by Top 6 Streaming Services from 2000 - 2021", 
       x = "", 
       y = "") + 
  guides(fill = guide_legend(title = NULL))+ 
  theme(panel.grid.major.x = element_blank(), 
        plot.title = element_text(family = "A", hjust = 0.5))
```
Final Graph: 

I chose to make this graph because I thought it would be interesting to see the breakdown of the Emmy wins by streaming services. The drastic switch streaming services have made from just being a video streaming platform to a creative/directing platform has changed the industry of streaming and is driving viewership. I chose to show only the comparisons of wins throughout the years via streaming services to show which have grown in popularity and to see if my own assumptions held true. I chose these side by side boxplots to better visualize the data, and I made year a categorical variable in order to see the different breakdowns between each year. Set2 fill palette was chosen for its nice and contrasting colors.
