---
title: "Tidy Tuesday 3"
description: "Data Visualization of RN Hourly Wages by State"
theme: cosmo
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE, error = TRUE)

library(ggmap)
library(maps)
library(tidyverse)
library(ggthemes) 
library(plotly)

```

```{r}
#nurses <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-10-05/nurses.csv')

```

```{r}
nurses <- read.csv("C:/Users/kates/OneDrive/Desktop/Advanced_data_science/TidyTuesday/nurses.csv")
```


```{r}
states_map <- map_data("state")

nurses <- nurses %>%
  mutate(state = tolower(State))
```


```{r}
nurse_map <- nurses %>%
  filter(Year == 2020) %>%
  ggplot() + 
  geom_map(aes(map_id = state, fill = Hourly_Wage_Avg),
           color = "grey",
           map = states_map) + 
  expand_limits(x = states_map$long, y= states_map$lat) + 
  theme_map() + 
  scale_fill_viridis_c(option  = "inferno") + 
                           theme_map() + 
                           theme(legend.background = element_blank()) +
  labs(title = "Average Hourly Wage for Registered Nurses per State",
       fill = "") 

ggplotly(nurse_map)
  
  
```

I chose to create this map, because I thought that an interactive map would make more sense as the nuances in the data were important for us to keep. I think that the data range on the legend on the side is a useful took to have as a reference for the average wages across the US, and the individual state hourly average is also in the plotly function. I also chose this distinctive color scheme, so it would show the difference in the averages. 

